My title

### 2024-11-03 paper/paper.qmd
Implemented survey in Google Forms and added link to qmd

The survey instrument itself focuses on six key areas: screening questions to identify likely voters, voting intentions (including direct questions about Trump vs. Harris preferences), political preferences, demographics, issue priorities, and media consumption patterns. We've implemented this survey design in Google Forms, which can be found here: [Link to be added]

@@

## Idealised survey
The survey, made using Google Forms, is linked here:
Note that the questions are identical for both the phone and online surveys bar q6.
A copy of the survey that is identical to the one implemented in the Google Forms above is presented below:
Thank you for participating in this survey about the 2024 U.S. Presidential Election. This survey is part of a research project at the University of Toronto studying voting intentions and political attitudes.

@@

Your responses will be kept confidential and used only for research purposes. You may skip any questions you prefer not to answer, though complete responses are most helpful for our research.

@@

Q5. If the 2024 presidential election were held today, and the candidates were Donald Trump (Republican) and Kamala Harris (Democrat), who would you vote for?

Donald Trump
Kamala Harris
Another candidate (please specify)
Would not vote
Not sure

@@

POLITICAL PREFERENCES:
Q7. Generally speaking, do you consider yourself a:

Republican
Democrat
Independent
Something else (please specify)

@@

Excellent
Good
Fair
Poor
Very poor

@@

For each of the following issues, please indicate whether you think Donald Trump or Kamala Harris would do a better job handling it:

@@

Donald Trump would do better
Kamala Harris would do better
No difference
Not sure

Q11. Immigration:
[Same options]
Q12. National security:
[Same options]
Q13. Healthcare:
[Same options]

MEDIA CONSUMPTION:
Q14. Where do you most often get your news about politics? (Select all that apply)

@@

Q15. How many hours per day do you typically spend following news about politics?

@@

DEMOGRAPHICS:
Q16. What is your age?

@@

Q17. What is your gender?

@@

Q18. What is your race/ethnicity? (Select all that apply)

@@

Q19. What is the highest level of education you have completed?

@@

Q20. What was your total household income before taxes in 2023?

@@

CONSISTENCY CHECK:
Q21. Looking ahead to November 2024, if Donald Trump is the Republican nominee and Kamala Harris is the Democratic nominee, how do you think you will vote?

Donald Trump
Kamala Harris
Another candidate (please specify)
Would not vote
Not sure

[END OF SURVEY]
Thank you for completing this survey about the 2024 U.S. Presidential Election. Your responses will help us better understand voter preferences and political attitudes across the country.
If you have any questions about this research or would like to be informed about the results, please contact andrew.goh@mail.utoronto.ca.
Your time and participation is greatly appreciated.
# Additional data details

>>>>

The survey instrument itself focuses on six key areas: screening questions to identify likely voters, voting intentions (including direct questions about Trump vs. Harris preferences), political preferences, demographics, issue priorities, and media consumption patterns. We've implemented this survey design in Google Forms, which can be found here: https://forms.gle/pk7vDiMHwEGLMK849

@@

## Idealised survey
The survey, made using Google Forms, is linked here: https://forms.gle/pk7vDiMHwEGLMK849
Note that the questions are identical for both the phone and online surveys bar q6.
A copy of the survey that is identical to the one implemented in the Google Forms above is presented below:
Thank you for participating in this survey about the 2024 U.S. Presidential Election. This survey is part of a research project at the University of Toronto studying voting intentions and political attitudes.

@@

Your responses will be kept confidential and used only for research purposes. Email information, and any other information that may personally identify you, is not gathered. You may skip any questions you prefer not to answer, though complete responses are most helpful for our research.

@@

Q5. If the 2024 presidential election were held today, and the candidates were Kamala Harris (Democrat) and Donald Trump (Republican), who would you vote for?

Kamala Harris
Donald Trump
Another candidate (please specify)
Would not vote
Not sure

@@

POLITICAL PREFERENCES:
Q7. Generally speaking, you consider yourself a:

Democrat
Republican
Independent
Something else (please specify)

@@

Very poor
Poor
Fair
Good
Excellent

@@

For each of the following issues, please indicate whether you think Kamala Harris or Donald Trump would do a better job handling it:

@@

Kamala Harris would do better
Donald Trump would do better
No difference
Not sure

Q11. Human rights and freedom of speech:
[Same options]
Q12. Abortion:
[Same options]
Q13. Healthcare:
[Same options]
Q14. Immigration:
[Same options]
Q15. National security:
[Same options]

MEDIA CONSUMPTION:
Q16. Where do you most often get your news about politics? (Select all that apply)

@@

Q17. How many hours per day do you typically spend following news about politics?

@@

DEMOGRAPHICS:
Q18. What is your age?

@@

Q19. What is your gender?

@@

Q20. What is your race/ethnicity? (Select all that apply)

@@

Q21. What is the highest level of education you have completed?

@@

Q22. What was your total household income before taxes in 2023?

@@

CONSISTENCY CHECK:
Q23. Looking ahead to November 2024, if Kamala Harris is the Democratic nominee and Donald Trump is the Republican nominee, how do you think you will vote?

Kamala Harris
Donald Trump
Another candidate (please specify)
Would not vote
Not sure

[END OF SURVEY]
Thank you for completing this survey about the 2024 U.S. Presidential Election. Your responses will help us better understand voter preferences and political attitudes across the country.
If you have any questions about this research or would like to be informed about the results, please contact andrew.goh@mail.utoronto.ca.
Your time and participation is greatly appreciated.

# Additional data details
